### 2014-04-10 stat246/hw1.tex
s1 done

Rewriting the conditional probabilities, the prediction is then $\text{argmax}\left(\lto P(X|Y=2)P(Y=2), \lot P(X|Y=1)P(Y=1)\right)$. Setting these equal to find the boundary, we have
\[\lto \pi_2\exp\left((x-\mu_2)^2/(2\sigma^2)\right)=\lot\pi_1\exp\left((x-\mu_1)^2/(2\sigma^2)\right)\]
Solving for $x$, we obtain
\[x^*=\frac{2\sigma\log\frac{\lot\pi_1}{\lto\pi_2}+\mu_2^2-\mu_1^2}{2(\mu_2-\mu_1)}\]
Now, if we choose $\lot$ to be proportional to $\pi_1^{-1}$ and choose $\lto$ to be proportional to $\pi_2^{-1}$ (possibly with different constants), we will avoid the degeneracy problem.
\ssn{e}
Using these values, we have that $x^*=1$, so plugging into the expression for the error rate from (b) gives $0.5\Phi(-1)+0.5-0.5\Phi(1)=0.1587$
}
\subsection*{4}
The expected loss of some decision function $\h{H}$ is $E_{X, Y}(L(\h{H}(x), Y)$. Writing out the integral gives
\[\int_{\rn^n}\sum_{k=1}^KL(\h{H}(x), k)p(x, k) dx=\int_{\rn^n}p(x)\sum_{k=1}^KL(\h{H}(x), k)P(k|x)dx\]

>>>>

Rewriting the conditional probabilities, the prediction is then $\text{argmax}\left(\lto P(X|Y=2)P(Y=2), \lot P(X|Y=1)P(Y=1)\right)$. Setting these equal to find the boundary, we have
\[\lto \pi_2\exp\left((x-\mu_2)^2/(2\sigma^2)\right)=\lot\pi_1\exp\left((x-\mu_1)^2/(2\sigma^2)\right)\]
Solving for $x$, we obtain
\[x^*=\frac{2\sigma\log\frac{\lot\pi_1}{\lto\pi_2}+\mu_2^2-\mu_1^2}{2(\mu_2-\mu_1)}\]
Now, if we choose $\lot$ to be proportional to $\pi_1^{-1}$ and choose $\lto$ to be proportional to $\pi_2^{-1}$ (possibly with different constants), we will avoid the degeneracy problem.
\ssn{e}
Using these values, we have that $x^*=1$, so plugging into the expression for the error rate from (b) gives $0.5\Phi(-1)+0.5-0.5\Phi(1)=0.1587$.

If we estimate the two means as $\conj{x_1}$ and $\conj{x_2}$, using the expression from (a), the decision boundary would be 
{
    \nc{\cxi}{\conj{x_1}}
    \nc{\cxii}{\conj{x_2}}
    $\frac{\cxii^2-\cxi^2}{2(\cxii-\cxi)}$
}

Code for the computation of error rates from the samples is attached, using the expression from (b). A histogram follows.

\includegraphics[width=0.6\textwidth]{hw1_files/p3.png}

}
\subsection*{4}
The expected loss of some decision function $\h{H}$ is $E_{X, Y}(L(\h{H}(x), Y)$. Writing out the integral gives
\[\int_{\rn^n}\sum_{k=1}^KL(\h{H}(x), k)p(x, k) dx=\int_{\rn^n}p(x)\sum_{k=1}^KL(\h{H}(x), k)P(k|x)dx\]
